### 2017-01-04 robust-software.tex
Clarifying our meaning of robust

Software produced for research,
published and otherwise,
suffers from a number of common problems
that make it difficult or impossible to run outside the original institution,
or even off the primary developer's computer.
We present ten simple rules to make such software robust enough to run anywhere,
and inspire confidence in your reproducibility,
and thereby delight your users and collaborators.

@@

So what \emph{is} ``robust'' software?
In brief, it:

\begin{itemize}
\item
  works for users other than the original author;
\item
  is kept under version control;
\item
  can be installed on more than one computer or account with relative ease;
\item
  has well-defined input and output formats;
\item
  has documentation that describes what its dependencies are, how to
  install it, and what the options are; and
\item
  comes with enough tests to show that it actually runs.
\end{itemize}

These simple rules don't just ensure that the software will run for other people;
they are also necessary steps toward creating a reusable
library that can be shared and reused through a site like CPAN or CRAN.  They are
generic and can be applied to all languages, libraries, packages,
documentation styles, and operating systems for both closed-source and
open-source software.  
Whether the aim is as simple as sharing the
code with collaborators or as complex as using the software in a
production analysis environment, increasing the robustness of your
software decreases headaches all around.

>>>>

Software produced for research,
published and otherwise,
suffers from a number of common problems
that make it difficult or impossible to run outside the original institution,
or even off the primary developer's computer.
We present ten simple rules to make such software robust enough to be run by anyone,
anywhere,
and thereby delight your users and collaborators.

@@

So what \emph{is} ``robust'' software?
We implied above that it is software that works for people other than the original author,
on machines other than its creator's.
More specifically, we mean that:

\begin{itemize}
\item
  it can be installed on more than one computer with relative ease,
\item
  it works as advertised, and
\item
  it can be integrated with other tools.
\end{itemize}

Our rules are generic and can be applied to all languages, libraries, packages,
documentation styles, and operating systems for both closed-source and open-source software.  
They are also necessary steps toward making computational research reproducible:
after all,
if the tools and libraries used to produce a result cannot be run by others,
they cannot verify or build on published results.
